Proof part 1: 3 layers

### 2023-10-09 Blaise.tex
blaise

	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the $f(x) \geq 0$ abstraction only) for node $x$, 
	and $\underline{f}(x)$ its lower bound approximation function.
\end{itemize}

We want to show that for any $c$ in the output layer (3rd layer), there exist 
input $\bar{Y}$ such that $W_{\bar{Y}}(x) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
 $\underline{Y}$ such that $W_{\underline{Y}}(x) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.

@@

First, we compute the bounds obtained by DeepPoly.
The case of the lower bound is symetrical (because the abstraction $f(x)\geq 0$ is used, ensuring that the lower bound of $f(x)$ is reached at 0).

The DeepPoly upper bound of $x$ can be expressed by the following steps:

\begin{align}
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(b_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(b_i)+B_x\\
 \rightarrow&\sum_{W_{xb_i}<0}W_{xb_i}\underline{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\bar{f_i}(\sum_{c_j}W_{b_ic_j}c_j+B_i)+B_x\\
 =& C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
 =& C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
 \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\
 &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
\end{align}

>>>>

	\item We denote by $\bar{f}(x)$ the upper bound approximation function of DeepPoly (using the ReLU$(x) \geq 0$ abstraction only) for node $x$, 
	and $\underline{f}(x)$ its lower bound approximation function.
\end{itemize}

We want to show that for any $c$ in the output layer (3rd layer), there exist 
input $\bar{Y}$ such that $W_{\bar{Y}}(c) = \bar{f}(c)(\bar{Y}) = \min_Y \bar{f}(c)(Y)$, and 
 $\underline{Y}$ such that $W_{\underline{Y}}(c) = \underline{f}(c)(\underline{Y}) = \min_Y \underline{f}(c)(Y)$.

@@

First, we compute the bounds obtained by DeepPoly.
The case of the lower bound is symetrical (because the abstraction ReLU$(x)\geq 0$ is used, ensuring that the lower bound of $\underline{f}(x)$ is reached at 0).

The DeepPoly function for $c$ can be expressed by the following steps:

First, we particition the set of indices $i$ for $b_i$ as $I,I_0,I^+,I^-$ with:
\begin{itemize}
	\item $i \in I$ if the sign of $b_i^-=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)(Y)=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ and
	$\underline{f}(b_i^+)=\underline{f}(b_i^-)$, and else:
	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,
	and else:
	\item $i \in I^+$ if $\alpha_{b_i c}>0$, and:
	\item $i \in I^-$ if $\alpha_{b_i c}<0$.
	\end{itemize}

Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.

Then we have:
\begin{align*}
	&\bar{f}(c)(Y) = 
	\sum_{i \in I} \sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}
	+ \sum_{i \in I^+} \alpha_{b_i c} \cdot \bar{f_i}(ReLU(\sum_{j} \alpha_{a_j b_i} a_j + B_{b_i}))(Y)+ B_c 
	\end{align*}

Now,

 \begin{align}
 &= C+\sum_{W_{xb_i}<0}W_{xb_i}\cdot\underline{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)+\sum_{W_{xb_i}>0}W_{xb_i}\cdot\bar{k_i}\cdot(\sum_{c_j}W_{b_ic_j}c_j+B_i)\\
 &= C+\sum_{c_j}c_j\cdot\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\\
 \rightarrow& C+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i<0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot l(c_j)\\
 &+\sum_{\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i>0}\sum_{b_i}W_{xb_i}W_{b_ic_j}\cdot K_i\cdot u(c_j)
\end{align}
